Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-27 nge.tex
Iterate 6.1

\subsection{Rationale} \aanote{I think that the names of the states should be
removed. They are meaningless without the figures. I left them just in case we
decide to reintroduce the figures.}\mtnote{Done.} As seen in
\S\ref{sec:panda_deployment}, the absence of wide area network
\jhanote{admittedly i haven't read earlier section in question  carefully, but
i'm a bit confused about the use of "wide area". wide area is typically used for
cross data center}\mtnote{Every PanDA Pilot has to communicate with PanDA
Server. PanDA Server runs on dedicated resources, outside OLCF. Titan's worker
nodes cannot communicate with PanDA Server because their connectivity is limited
to Titan's network. Do you have a suggestion for an alternative to ``wide
area''?} connectivity on Titan's worker nodes was one of the main reasons for
PanDA Broker not to implement pilots. As discussed in \S\ref{sec:panda_titan},
the absence of pilots imposes the static coupling between MPI scripts submitted
to the PBS batch system and detector simulations, and development tailored to
each type of payload that needs to be executed.

This static coupling makes impossible to schedule multiple generations of
workload on the same PBS job. Specifically, once a number of detector
simulations are packaged into a PBS job and this job is queued on Titan, no
further simulations can be added to that job. New simulations have to be
packaged into a new PBS job that needs to be submitted to Titan on the base of
the backfill availability of that moment.

@@

Multiple generations would also help with relaxing two assumptions of the
current execution model: knowing the number of simulations before submitting the
MPI script, having a fixed amount of events per simulation (100 at the moment).
Pilots would enable the scheduling of simulations independently from whether
they were available at the moment of submitting the pilot. Further, simulations
with a varying number of events could be scheduled on a pilot, depending on the
amount of remaining walltime and the distribution of execution time per event,
as shown in \S\ref{ssec:panda_titan}, Figure~\ref{fig:100event-distrib}. This
capabilities would be particularly useful to increase the PanDA Broker
efficiency for availabilities with a wide delta between the number of cores and
walltime.

>>>>

\subsection{Rationale} \aanote{I think that the names of the states should be
removed. They are meaningless without the figures. I left them just in case we
decide to reintroduce the figures.}\mtnote{Done.}

\jhanote{admittedly i haven't read earlier section in question  carefully, but
i'm a bit confused about the use of "wide area". wide area is typically used for
cross data center}\mtnote{Every PanDA Pilot has to communicate with PanDA
Server. PanDA Server runs on dedicated resources, outside OLCF. Titan's worker
nodes cannot communicate with PanDA Server because their connectivity is limited
to Titan's network. Do you have a suggestion for an alternative to ``wide
area''?}

As seen in \S\ref{sec:panda_deployment}, PanDA Broker was deployed on DTNs
because of the absence of wide area network connectivity on Titan's worker
nodes. The lack of pilot capabilities impacts both the efficiency and the
flexibility of PanDA's execution process. Pilots could help to improve
efficiency by increasing throughput and by enabling better use of backfill
utilization. Further, pilots makes easier to support heterogeneous workloads.

As discussed in \S\ref{sec:panda_titan}, the absence of pilots imposes the
static coupling between MPI scripts submitted to the PBS batch system and
detector simulations. This makes impossible to schedule multiple generations of
workload on the same PBS job: Once a number of detector simulations are packaged
into a PBS job and this job is queued on Titan, no further simulations can be
added to that job. New simulations have to be packaged into a new PBS job that
needs to be submitted to Titan on the base of the backfill availability of that
moment.

@@

Multiple generations would also help with relaxing two assumptions of the
current execution model: knowing the number of simulations before submitting the
MPI script, and having a fixed amount of events per simulation (100 at the
moment). Pilots would enable the scheduling of simulations independently from
whether they were available at the moment of submitting the pilot. Further,
simulations with a varying number of events could be scheduled on a pilot,
depending on the amount of remaining walltime and the distribution of execution
time per event, as shown in \S\ref{ssec:panda_titan},
Figure~\ref{fig:100event-distrib}. This capabilities would be particularly
useful to increase the PanDA Broker efficiency for availabilities with a wide
delta between the number of cores and walltime.
